---
title: "Untitled"
author: "柯宥圻"
date: "2023-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW4
### QUESTION 4
I calculate the T2 value by hand on the second page, and I just use the package to confirm whether I calculate right.


```{r}
#Question 4
data <- read.csv(file="C:/Users/user/Desktop/HW4-4.csv")
data
# install.packages("ICSNP")
library(ICSNP)
HotellingsT2(data, mu=c(7,11))
```
since the P value is 0.1803, we can't reject H0 and say that true location is not equal to c(7,11).

## Question 5
we want to know the relationship between man's turtle and woman's turtle. Therefore, we have three dimensions. We take MANOVA to see if the two populations are equal.
```{r}
turtle <- read.csv(file="C:/Users/user/Desktop/HW4-5.csv")
turtle
# install.packages("dplyr")
set.seed(1234)
dplyr::sample_n(turtle, 48)
res.man <- manova(cbind(length, width, height) ~ sex, data = turtle)
summary(res.man)
```
By using MANOVA, it can be seen that the P value is quite small, and the variables are not all the same. We use the summary.aov() to see which differ.
```{r}
summary.aov(res.man)
```
as the code shown, the three variables are all highly significantly different among those drawn turtles.

### Question 6-a

we want to study whether the spectral reflectance at wavalength 560nm and 720nm has the species effect and nutrient effect on the alpha 5%. We first do the MANOVA test to see whether the data has these effect.

```{r}
CM_mean <- data.frame(x1 = c(10.35, 13.41, 7.78, 10.4, 17.78, 10.4),
                      x2 = c(25.93, 38.63, 25.15, 24.25, 41.45, 29.2),
                      species = factor(c(1, 2, 3, 1, 2, 3)),
                      nutrient = factor(c(1,1,1,2,2,2)))

# MANOVA for the species effect
species_manova <- manova(cbind(x1, x2) ~ species, data = CM_mean)
summary(species_manova)

# MANOVA for the nutrient effect
nutrient_manova <- manova(cbind(x1, x2) ~ nutrient, data = CM_mean)
summary(nutrient_manova)
```

Based on the MANOVA results, we can conclude that there is no significant species effect on the spectral reflectance, but no significant nutrient effect.

### Question 6-b

Based on the MANOVA results, we fail to reject the null hypothesis for the species effect, but we can still perform the two-way ANOVAs for both the 560CM and the 720CM observations to check for any significant effects of the nutrients and their interaction.
```{r}
# two-way ANOVA for 560CM
anov560 <- aov(CM_mean$x1 ~ CM_mean$species + CM_mean$nutrient + CM_mean$species:CM_mean$nutrient)
summary(anov560)

# two-way ANOVA for 720CM
anov720 <- aov(CM_mean$x2 ~ CM_mean$species + CM_mean$nutrient + CM_mean$species:CM_mean$nutrient)
summary(anov720)
```

The output of each ANOVA includes the Sum of Squares (SS), the Degrees of Freedom (DF), the Mean Square (MS), the F statistic, and the p-value for each main effect and interaction.

Here is the expected output:

```                               
                                 Df Sum Sq Mean Sq F value  Pr(>F)   
CM_mean$species                   2  47.48  23.738  1.0357 0.42410   
CM_mean$nutrient                  1   8.26   8.260  0.3596 0.57989   
CM_mean$species:CM_mean$nutrient  2   4.72   2.361  0.1026 0.90992   
Residuals                         3  73.17  24.389                    
                             
                                 Df Sum Sq Mean Sq F value  Pr(>F)   
CM_mean$species                   2 262.24 131.120  2.0359 0.22498   
CM_mean$nutrient                  1   4.49   4.490  0.0698 0.80434   
CM_mean$species:CM_mean$nutrient  2   9.10   4.550  0.0707 0.80155   
Residuals                         3 158.13  52.710                    
```                               

The results of the MANOVA test and the two-way ANOVAs are consistent with each other. Specifically, the species effect was not significant in either the MANOVA or the two-way ANOVAs for either the 560CM or the 720CM observations. The nutrient effect was not significant in either the MANOVA or the two-way ANOVAs for either the 560CM or the 720CM observations. There was also no significant interaction effect in either of the two-way ANOVAs.